Trans-Dimensional Inference for Gravitational Lens Substructures

### 2015-06-06 Papers/ms.tex
David's figure fixes
RJObject para, Green reference

% Packages:
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{xspace}
\usepackage{dsfont}
\usepackage[utf8]{inputenc}
\usepackage{caption}
\usepackage{subcaption} % subfigures
\usepackage{float}

@@

Since the model is not of fixed dimension (the number of source and lens
``blobs'' is unknown), we implemented the MCMC using the {\tt RJObject}
\citep{rjobject} software, a C++ library for implementing trans-dimensional
MCMC with hierarchically-specified priors, and doing the sampling with the
Diffusive Nested Sampling algorithm \citep{dnest}. Previous astronomical
applications of {\tt RJObject} include \citet{magnetron}
and~\citep{exoplanet}.

\section{The Cosmic Horseshoe}
As a demonstration the method is the applied to the Cosmic Horseshoe INT data. 
The field of view of the image is $15.3180" \times 15.3180"$, and the size is $46 \times 46$ pixels, therefore one pixel is equivalent to $0.33"$. \\
The method discussed  in the previous section is applied to two models, the first model consist of a flexible source and a Singular Isothermal Elliptical(SIE) model for the lens.  This model is similar to models used in previous work \cite{Belokurov2007} \cite{Dye2008}. 
The second model has in addition to the flexible source and SIE, also possible satellites. \\
The amount of added satellites is automatically determined by the program. If models the addition of an satellite galaxies gives a higher probability it will be preferred over then model without satellite galaxies.  \\
In both models the SIE is specified by the usual parameters: the location of the NIE ($x_c$,$y_c$), b, axis ratio $f$\footnote{in the code denoted with $q$},  the core radius$\zeta$, $\theta$, shear $\gamma$, and $\theta_{\gamma}$ \cite{kormann_schneider_1994}.\\
One of the firsts step in applying Bayesian analysis is providing good prior distribution for the parameters. 
The chosen prior probability distributions are displayed in table \ref{table:1}. The parameters which are not listed in table 
\ref{table:1} depend on parameters which are listed.

@@

 \begin{figure}[!h]
 \hspace{20pt}
\begin{subfigure}{.45\textwidth}
  \centering
  \includegraphics[width=0.75\linewidth,angle=90]{log_mass_SIE_no_blobs.eps}
\parbox{0.8\linewidth}{\caption{The log of the SIE mass within the critical curve  for model A.  \label{fig:sub1} }}
\end{subfigure}%
\begin{subfigure}{.45\textwidth}
  \centering
  \includegraphics[width=0.75\linewidth,angle=90]{log_mass_SIE.eps}
   \parbox{0.8\linewidth}{\caption{The log of the SIE mass within the critical curve for model B.   \label{fig:sub2}}}
\end{subfigure}
   \end{figure}

@@

>>>>

% Packages:
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{xspace}
%\usepackage{dsfont}
\usepackage[utf8]{inputenc}
\usepackage{caption}
\usepackage{subcaption} % subfigures
\usepackage{float}

\usepackage{epstopdf}

@@

Since the model is not of fixed dimension (the number of source and lens
``blobs'' is unknown), we used a trans-dimensional MCMC sampler based on
reversible jump MCMC \citep{green}. We implemented the MCMC using the
{\tt RJObject} software \citep{rjobject}, a C++ library for implementing trans-dimensional
MCMC with hierarchically-specified priors, and doing the sampling with the
Diffusive Nested Sampling algorithm \citep{dnest}. Previous astronomical
applications of {\tt RJObject} include \citet{magnetron}
and~\citep{exoplanet}. Proposal moves for the parameters (positions and masses
of the source and lens blobs), and birth/death moves to add or remove blobs
to the source or lens, are handled internally by {\tt RJObject}.

\section{The Cosmic Horseshoe}
As a demonstration the method is the applied to the Cosmic Horseshoe INT data. 
The field of view of the image is $15.3180" \times 15.3180"$, and the size is $46 \times 46$ pixels, therefore one pixel is equivalent to $0.33"$. \\
The method discussed  in the previous section is applied to two models, the first model consist of a flexible source and a Singular Isothermal Elliptical(SIE) model for the lens. This model is has been used often  \cite{Dye2008}, \cite{schneider_falcoa_Ehlers_1994},      . 
The second model has in addition to the flexible source and SIE, also possible satellites. \\
The amount of added satellites is automatically determined by the program. If models the addition of an satellite galaxies gives a higher probability it will be preferred over then model without satellite galaxies.  \\
In both models the SIE is specified by the usual parameters: the location of the NIE ($x_c$,$y_c$), b, axis ratio $f$\footnote{in the code denoted with $q$},  the core radius$\zeta$, $\theta$, shear $\gamma$, and $\theta_{\gamma}$ \cite{kormann_schneider_1994}.\\
One of the firsts step in applying Bayesian analysis is providing good prior distribution for the parameters. 
The chosen prior probability distributions are displayed in table \ref{table:1}. The parameters which are not listed in table 
\ref{table:1} depend on parameters which are listed.

@@

 \begin{figure*}
% \hspace{20pt}
\begin{subfigure}{.45\textwidth}
  \centering
  \includegraphics[width=0.75\linewidth,angle=90]{log_mass_SIE_no_blobs.eps}
\parbox{0.8\linewidth}{\caption{The log of the SIE mass within the critical curve  for model A.  \label{fig:sub1} }}
\end{subfigure}%
\begin{subfigure}{.45\textwidth}
  \centering
  \includegraphics[width=0.75\linewidth,angle=90]{log_mass_SIE.eps}
   \parbox{0.8\linewidth}{\caption{The log of the SIE mass within the critical curve for model B.   \label{fig:sub2}}}
\end{subfigure}
   \end{figure*}

@@

\bibitem[\protect\citeauthoryear{Green}{1995}]{rjmcmc}
Green, P.~J., 1995, Reversible Jump Markov Chain Monte Carlo Computation and Bayesian Model Determination, Biometrika 82 (4): 711–732.
